---
title: "Abess"
author: "Ryan Walsh"
date: "2022-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

R Assignment 2 (Individual) 

 

Download this dataset from Canvas and use it for this assignment.  
```{r}
library(tidyverse)
df <- read.csv("Abess.csv")
```

  

Rename the variable “var1” to “Earning”.  
```{r}
names(df)[2] <- 'Earning'
```

Check whether there are any missing values in the dataset.  
```{r}
df %>% is.na() %>% colSums()
```

Check the “Education” variable for abnormal values. Replace those with “NA”. 
```{r}
table(df$Education)
#we believe that 99 is a invalid value
df$Education<- case_when(df$Education == 99 ~ "NA",TRUE ~ as.character(df$Education))

```

Check the “Earning” variable for abnormal values. Replace those with “NA”. 

```{r}
df$Earning<- case_when(df$Earning == 99 ~ "NA",TRUE ~ as.character(df$Earning))
```

Create a new dataset omitting the missing values. Use the newly created dataset for the rest of the questions. 
```{r}
df1 <- drop_na(df)
df1 %>% is.na() %>% colSums()

```

Create a dummy variable called “Female” which equals 1 if Gender is Female, zero otherwise.  
```{r}
df$sex <- case_when(df$Gender == "Female" ~ 1, TRUE ~ 0)
```

Create a dummy variable called “Urban” which equals 1 if Location is Urban, zero otherwise. 
```{r}
df$Location1 <- case_when(df$Location == "Urban" ~ 1, TRUE ~ 0)

```


Find the mean and median earning.  
```{r}
df1 <- df %>% filter(!Earning == "NA")
df1 %>% summarise(mean = mean(Earning))
df1 %>% summarise(median = median(Earning))
```


Does earning vary by gender and location? Find the mean by different gender and location.  
```{r}
df1 %>% filter(sex==0) %>% 
        group_by(sex,Location1,Earning) %>% 
        summarise(mean= mean(Earning)) %>% 
        arrange(-mean)

df1 %>% filter(sex==1) %>% 
        group_by(sex,Location1,Earning) %>% 
        summarise(mean= mean(Earning)) %>% 
        arrange(-mean)

df1 %>% filter(Location1==0) %>% 
        group_by(sex,Location1,Earning) %>% 
        summarise(mean= mean(Earning)) %>% 
        arrange(-mean)
df1 %>% filter(Location1==1) %>% 
        group_by(sex,Location1,Earning) %>% 
        summarise(mean= mean(Earning)) %>% 
        arrange(-mean)

```

Are the means of earning statistically different for male and female?  

 
Are the means of education statistically different for urban and rural?  

Create a scatter plot of earning and education variables. Label properly. Save the file on your computer.  
```{r}
gg <- df %>% 
  ggplot()+ 
  geom_point(aes(x=Education, y=Earning))
ggsave(filename = 'Abess.png', plot = gg)

```

Add a fitted line on the previous graph.  
```{r}
gg1 <- df %>% 
  ggplot()+ 
  geom_point(aes(x=Education, y=Earning))+geom_smooth(method = "lm",se = FALSE)

#ggsave(filename = 'Abess1.png', plot = gg1)
```

Are earning and education correlated? Find the correlation coefficient. Test whether the correlation statistically significant.  

```{r}
MAPE <-  function(y_actual, y_predict){
  mean(abs((y_actual-y_predict)/y_actual))*100
}
RSQUARE = function(y_actual,y_predict){
  cor(y_actual,y_predict)^2
}
```


 

Run a regression for the following regression equation:  

Earningi=β0+β1(Femalei)+εi
Earningi=𝛽0+𝛽1Femalei+𝜀i
 
```{r}
library(ggplot2)
library(dplyr)
library(broom)
library(ggpubr)

new_df <- df %>% filter(sex==0)

summary(new_df)
new_df <- drop_na(new_df)
#lm <- lm(Earning~sex,data=new_df)
#summary(lm)
```


How would you interpret the estimated constant coefficient (
βˆ0
𝛽^0
 
)? How does the estimated constant coefficient compare to the mean of male earning you found in (10)?   

How would you interpret the estimated Female coefficient (
βˆ1
𝛽^1
 
)? 

 

Run a regression for the following regression equation:  

[Equation] 

How would you interpret the estimated constant coefficient ([Equation])? How does the estimated constant coefficient compare to the mean of urban earning you found in (10)?   

 

Run a regression for the following regression equation:  

[Equation] 

How would you interpret the estimated constant coefficient ([Equation])?  

How would you interpret the estimated Education coefficient ([Equation])?  

 

Create an interaction term called “Education_Female” by multiplying “Education” and “Female”.  

Page Break
 

Run a regression for the following regression equation:  

[Equation] 

How would you interpret [Equation]?  

How would you interpret [Equation]?  

How would you interpret [Equation]? 

How would you interpret [Equation]? 

 

Get the standard error and t statistics of the estimated coefficients. Is estimated education coefficient statistically significant? 

 Output your regression results in a table format in csv or txt or xls or doc. Use that output and create a publication quality result table.  

 

Submit the R code file and a word file with answers to the questions (e.g., 10, 11, 14, 15, 19), graph (from 12) and table (from 21).  