
---
output: # rmarkdown::github_document
  html_document:
  pdf_document: default
  word_document: default
title: "Assignment 4 - Extra Credits"
---

***How to do it?***: 

- Open the Rmarkdown file of this assignment ([link](assignment4_extra_credits.Rmd)) in Rstudio. 

- Right under each **question**, insert  a code chunk (you can use the hotkey `Ctrl + Alt + I` to add a code chunk) and code the solution for the question. 

- Notice that if there is `eval=FALSE` in the first line of the code chunk, the chunk will not be execute.

- `Knit` the rmarkdown file (hotkey: `Ctrl + Alt + K`) to export an html.  

-  Publish the html file to your Githiub Page. 

***Submission***: Submit the link on Github of the assignment to Canvas. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(message = FALSE)
```

-------

This assignment works with the [IMDB Top 1000 data](../data/imdb_top_1000.csv).  Find out more information about this data at [this link](https://www.kaggle.com/datasets/harshitshankhdhar/imdb-dataset-of-top-1000-movies-and-tv-shows).  Import the data and answer the following questions. 

1. List all the names of the columns of the data
```{r}
library(tidyverse)
df <- read_csv("imdb_top_1000.csv")
colnames(df)
ncol(df)
```

2. Which movies have the highest money earned (Gross)?
```{r}
library(tidyverse)
df %>% arrange(-Gross) %>% select(Gross)
```


3. What is the lowest rating (IMDB_Rating)?  List five movies have this lowest rating.
```{r}
head(df %>% select(IMDB_Rating, Series_Title) %>% arrange(min_rank(IMDB_Rating)),n = 5)
```


4. Which year have the most number of movies released in the list?  What is the total of money earned on that year?
```{r}
head(df %>% select(Released_Year,Gross) %>% arrange(min_rank(Released_Year),Gross),n = 10)

```


5. What is the total money earned per movies on average?
```{r}
df %>% summarise(mean(Gross, na.rm = TRUE))
```


6. Calculate the average number of votes by year. Calculate the average number of votes of movies that have IMDB rating greater than 9.
```{r}
df %>% group_by(Released_Year) %>% filter(IMDB_Rating > 9) %>% summarise(mean(No_of_Votes),Series_Title)
```


7. Calculate the average Meta score in 2020 of movies that have number of votes in the third quartile. 

```{r}

df %>%  filter(Released_Year == 2020) %>% summarise(mean(No_of_Votes))

```

8. (Optional - Challenging). The current `Runtime` variable is not a numeric. Use the `str_remove` function to remove ` min` from the variables then use `as.numeric` to convert the variable to numeric. Calculate the average running time in the 2010s. Calculate the correlation between running time and rating (adding `use="complete.obs"` in the `cor` function to ignore the missing values).  

9. We can use `select_if` to select columns satisfying a condition and use `summarise_if` to do calculation on columns satisfying a condition.  Try the follows to understand these functions. 

```{r}
library(tidyverse)
# Select only character columns
df %>% select_if(is.character)

# Calculate the median of all numeric columns
df %>% summarise_if(is.numeric, mean, na.rm=TRUE)
```


10. Implement the follows functions or combos. Drawing a comment or summary from each calculation. The codes in this question should be different from the codes used in other questions.

- select
```{r}
df %>% select(Runtime) %>% head(n=10)
```

- filter
```{r}
df %>% select(Released_Year) %>% filter(Released_Year > 1990) %>% head(n=10)
```

- mutate
```{r}
df %>% mutate(Meta_score = Meta_score / 100)
# %change meta score
```

- summarise
```{r}
df %>% summarise(Meta_score) %>% head(n=10)
```

- arrange
```{r}
df %>%  arrange(-Meta_score) %>% summarise(Star1) %>% head(n = 10)
```

- count
- count + arrange
- filter + count + arrange
```{r}
df  %>% filter(Released_Year == 1970) %>% arrange(-Gross) %>% summarise(Series_Title)
```

- group_by + summarise
```{r}
df %>% group_by(Genre) %>% summarise(Series_Title) %>% head(n = 10)
```

- filter + group_by + summarise
```{r}
df %>% filter(IMDB_Rating > 7) %>% group_by(Genre) %>% summarise(Series_Title) %>% head(n = 10)
```

- filter + group_by + summarise + arrange
```{r}
df %>% filter(IMDB_Rating > 7) %>% arrange(-No_of_Votes) %>% group_by(Genre) %>% summarise(Series_Title)  %>% head(n = 10)

```

