
---
title: "Titanic - Combination of Inputs"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: logo.png
    source_code: embed
    social: menu

runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
library(lubridate)
df <- read_csv('https://bryantstats.github.io/math421/data/titanic_final.csv')
df <- read_csv('diabetes.csv')
df$preg <- case_when(df$Pregnancies %in% c(1,2,3) ~ "Has been Pregnant",df$Pregnancies >= 4 ~"Above Average Pregnancies",df$Pregnancies == 0 ~"Never been pregnant")
df$out <- case_when(df$Outcome == 1 ~ "diabetes",df$Outcome == 0 ~"no diabetes")
df1 <- read_csv('Actual461Data.csv')
df1 <- drop_na(df1)
df1$date <- ymd(df1$sale_date)
df$out = factor(df$out)

preg<- unique(df$preg)
```

{.sidebar}
=======================================================================


```{r}
sliderInput(inputId = "Age_input",
            label = h2("Select Age Range for tabs 1 & 2"),
            min = min(df$Age, na.rm=TRUE),
            max = max(df$Age, na.rm=TRUE),
            value= c(21, 81))
```

```{r}
#tab 1
checkboxGroupInput(inputId = "pregnancy_input2", 
                   label = h3("Select pregnancy status for main tab 1"),
                   choices = preg, 
                   inline = TRUE,
                   selected = 'Has been Pregnant')




```

```{r}

selectInput(inputId = "outcome_input", 
            label = h4("Select dibetets outcome for main tab 2"),
            choices = df$out, 
            selected = "no diabetes")

radioButtons(inputId = "pregnancy_input", 
             label = h2("Select Pregnancy status for main tab 2"),
             choices = c("Has been Pregnant","Above Average Pregnancies","Never been pregnant"),
             inline = TRUE,
             selected = "Never been pregnant")
```





```{r}
dateRangeInput(inputId = "date_input", 
               label = h4("Date range for main tab 3"), 
               start = min(df1$date), 
               end = max(df1$date),
               min = min(df1$date), 
               max = max(df1$date))
```



Main Tab 1
=======================================================================

Column {data-width=500, .tabset}
-----------------------------------------------------------------------

### Density Plot


```{r,eval=FALSE}
renderPlotly({
  p1 <- df
     %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% filter(preg==input$pregnancy_input) %>% 
    ggplot(aes(x=Age, color=preg))+
    geom_bar()
  ggplotly(p1)
})

```

```{r}
renderPlotly({
  p1 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(preg==input$pregnancy_input2) %>% 
    ggplot(aes(x=Age, color=preg))+
    geom_density()
  ggplotly(p1)
})
```
### Diabetes dat
```{r}
datatable(df, options = list(
  pageLength = 25
))

```

Column {data-width=500}
-----------------------------------------------------------------------

### Bar Plot

```{r}
renderPlotly({
  p2 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(preg==input$pregnancy_input2) %>% 
    ggplot(aes(x=Age, y = Insulin,fill=preg))+
    geom_col()
  ggplotly(p2)
})
```


Main Tab 2
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Density Plot

```{r}
renderPlotly({
  p2 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(out==input$outcome_input) %>% filter(preg==input$pregnancy_input) %>% 
    ggplot(aes(x=Age,fill=preg))+
    geom_density()
  ggplotly(p2)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### Bar plot

```{r}
renderPlotly({
  p2 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(out==input$outcome_input) %>% filter(preg==input$pregnancy_input) %>% 
    ggplot(aes(x=Age))+
    geom_bar()
  ggplotly(p2)
})
```

Main Tab 3
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### 461 brooklyn housing data

```{r}
#461 data
df1$salecat <-  case_when(df1$sale_price >= 527431 ~"above average sale",TRUE~"below average sale")
renderPlotly({
  p1 <- df1 %>% 
    filter(date > input$date_input[1], date < input$date_input[2])%>%  
    ggplot(aes(x=NumFloors,fill =salecat))+
    geom_bar()
  ggplotly(p1)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### brooklyn housing data

#### About Dataset

This is the dataset I am currently using in my 461 applied multivariate statistics project. This dataset is composed of the interquartile rangem with respect to sale price of 1 2 and 3 family homes located in Brooklyn New York City. This data set will be used to apply my knowledge in multivariate statistics through the application of statistical processes such as factor analysis PCA and then apply our dataset to models such as GLMs. This data set was created and uploaded by TOMMY WU on kaggle and his goal with the unwrangled data I worked with to get the current data set is as follows "I'm trying to make a Choropleth map over time of home sale prices by block in Brooklyn for the last 15 years to visualize gentrification. I have the entire dataset for all 5 boroughs of New York, but am starting with Brooklyn."







