
---
title: "Titanic - Combination of Inputs"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: logo.png
    source_code: embed
    social: menu

runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
library(lubridate)
df <- read_csv('https://bryantstats.github.io/math421/data/titanic_final.csv')
df <- read_csv('diabetes.csv')
df$preg <- case_when(df$Pregnancies %in% c(1,2,3) ~ "Has been Pregnant",df$Pregnancies >= 4 ~"Above Average Pregnancies",df$Pregnancies == 0 ~"Never been pregnant")
df$out <- case_when(df$Outcome == 1 ~ "diabetes",df$Outcome == 0 ~"no diabetes")
df1 <- read_csv('Actual461Data.csv')
df1 <- drop_na(df1)
df1$date <- ymd(df1$sale_date)
df$out = factor(df$out)

preg<- unique(df$preg)
```

{.sidebar}
=======================================================================

The sinking of the Titanic is one of the most infamous shipwrecks in history. While there was some element of luck involved in surviving, it seems some groups of people were more likely to survive than others.  Select the input for the plots. 


```{r}
#tab 1
sliderInput(inputId = "Age_input",
            label = h2("Select Age Range"),
            min = min(df$Age, na.rm=TRUE),
            max = max(df$Age, na.rm=TRUE),
            value= c(21, 81))



radioButtons(inputId = "pregnancy_input", 
             label = h2("Select Pregnancy status"),
             choices = c("Has been Pregnant","Above Average Pregnancies","Never been pregnant"),
             inline = TRUE,
             selected = "Never been pregnant")
#tab 2
checkboxGroupInput(inputId = "pregnancy_input2", 
                   label = h3("Select pregnancy status"),
                   choices = preg, 
                   inline = TRUE,
                   selected = 'Has been Pregnant')

selectInput(inputId = "outcome_input", 
            label = h4("Select dibetets outcome"),
            choices = df$out, 
            selected = "no diabetes")

#tab 3

dateRangeInput(inputId = "date_input", 
               label = h4("Date range"), 
               start = min(df1$date), 
               end = max(df1$date),
               min = min(df1$date), 
               max = max(df1$date))

```

Main Tab 1
=======================================================================

Column {data-width=500, .tabset}
-----------------------------------------------------------------------

### Density Plot


```{r,eval=FALSE}
renderPlotly({
  p1 <- df
     %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% filter(preg==input$pregnancy_input) %>% 
    ggplot(aes(x=Age, color=preg))+
    geom_bar()
  ggplotly(p1)
})

```

```{r}
renderPlotly({
  p1 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(preg==input$pregnancy_input) %>% 
    ggplot(aes(x=Age, color=preg))+
    geom_density()
  ggplotly(p1)
})
```
### column tab 2 
```{r}
datatable(df, options = list(
  pageLength = 25
))

```

Column {data-width=500}
-----------------------------------------------------------------------

### Bar Plot

```{r}
renderPlotly({
  p2 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(preg==input$pregnancy_input2) %>% 
    ggplot(aes(x=Age, y = Insulin,fill=preg))+
    geom_col()
  ggplotly(p2)
})
```


Main Tab 2
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Density Plot

```{r}
renderPlotly({
  p2 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(out==input$outcome_input) %>% filter(preg==input$pregnancy_input2) %>% 
    ggplot(aes(x=Age,fill=preg))+
    geom_density()
  ggplotly(p2)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### What is Density Plot?

```{r}
renderPlotly({
  p2 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(out==input$outcome_input) %>% filter(preg==input$pregnancy_input) %>% 
    ggplot(aes(x=Age))+
    geom_bar()
  ggplotly(p2)
})
```





Main Tab 3
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### 461 brooklyn housing data

```{r}
#461 data
df1$salecat <-  case_when(df1$sale_price >= 527431 ~"above average sale",TRUE~"below average sale")
renderPlotly({
  p1 <- df1 %>% 
    filter(date > input$date_input[1], date < input$date_input[2])%>%  
    ggplot(aes(x=NumFloors,fill =salecat))+
    geom_bar()
  ggplotly(p1)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### Text paragraph and image!

this is example text about how luke is bad at chess




