
---
title: "Diabetes data"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: logo.png
    source_code: embed
    social: menu
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
library(rsconnect)
# Create a ggplot object
library(plotly)
df <- read_csv('diabetes.csv')
df$preg <- case_when(df$Pregnancies >= 1 ~ "Has been Pregnant",TRUE ~"Never been pregnant")
```

{.sidebar}
=======================================================================

### Diabetes dataset
- Link to Akshay Dattatray Khare kaggle upload [here](https://www.kaggle.com/datasets/akshaydattatraykhare/diabetes-dataset)


This dataset is originally from the National Institute of Diabetes and Digestive and Kidney
Diseases. The objective of the dataset is to diagnostically predict whether a patient has diabetes,
based on certain diagnostic measurements included in the dataset. Several constraints were placed
on the selection of these instances from a larger database. In particular, all patients here are females
at least 21 years old of Pima Indian heritage.2
From the data set in the (.csv) File We can find several variables, some of them are independent
(several medical predictor variables) and only one target dependent variable (Outcome).


Main Tab 1
=======================================================================

Column {data-width=500,data-height=1000 .tabset}
-----------------------------------------------------------------------



### Column Tab 1

```{r}
datatable(df, options = list(
  pageLength = 25
))
```


Column {data-width=500}
-----------------------------------------------------------------------


```{r}
df %>% ggplot(aes(x=Age,y=Pregnancies))+geom_point()
```



Main Tab 2
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------



#### 3. Example

```{r, echo=TRUE, eval=TRUE}

p <-df %>%  ggplot(aes(x=preg)) + geom_bar()
ggplotly(p)
```



Column {data-width=500}
-----------------------------------------------------------------------

### Row 1

```{r}
p <- df %>% ggplot(aes(x=Age, y = Glucose)) + geom_point()
ggplotly(p)
```



Main Tab 3
=======================================================================

```{r}
df %>% ggplot(aes(x = SkinThickness, y = BloodPressure))+geom_point()
```

