
---
title: "Titanic - Combination of Inputs"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    logo: logo.png
    source_code: embed
    social: menu

runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(flexdashboard)
library(tidyverse)
library(plotly)
library(knitr)
library(DT)
library(lubridate)
df <- read_csv('https://bryantstats.github.io/math421/data/titanic_final.csv')
df <- read_csv('diabetes.csv')
df$preg <- case_when(df$Pregnancies %in% c(1,2,3) ~ "Has been Pregnant",df$Pregnancies >= 4 ~"Above Average Pregnancies",df$Pregnancies == 0 ~"Never been pregnant")
df$out <- case_when(df$Outcome == 1 ~ "diabetes",df$Outcome == 0 ~"no diabetes")

df$out = factor(df$out)

preg<- unique(df$preg)
```

{.sidebar}
=======================================================================

The sinking of the Titanic is one of the most infamous shipwrecks in history. While there was some element of luck involved in surviving, it seems some groups of people were more likely to survive than others.  Select the input for the plots. 


```{r}
sliderInput(inputId = "Age_input",
            label = h2("Select Age Range"),
            min = min(df$Age, na.rm=TRUE),
            max = max(df$Age, na.rm=TRUE),
            value= c(21, 81))

selectInput(inputId = "outcome_input", 
            label = h3("Select dibetets outcome"),
            choices = df$out, 
            selected = "diabetes")

radioButtons(inputId = "pregnancy_input", 
             label = h2("Select Pregnancy status"),
             choices = c("Has been Pregnant","Above Average Pregnancies","Never been pregnant"),
             inline = TRUE,
             selected = "Never been pregnant")
```

Main Tab 1
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Density Plot


```{r,eval=FALSE}
renderPlotly({
  p1 <- df
     %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% filter(preg==input$pregnancy_input) %>% 
    ggplot(aes(x=Age, color=preg))+
    geom_bar()
  ggplotly(p1)
})

```

```{r}
renderPlotly({
  p1 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(preg==input$pregnancy_input) %>% 
    ggplot(aes(x=Age, color=preg))+
    geom_density()
  ggplotly(p1)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### Bar Plot

```{r}
renderPlotly({
  p2 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(preg==input$pregnancy_input) %>% 
    ggplot(aes(x=Age, y = Insulin,fill=preg))+
    geom_col()
  ggplotly(p2)
})
```


Main Tab 2
=======================================================================

Column {data-width=500}
-----------------------------------------------------------------------

### Density Plot

```{r}
renderPlotly({
  p2 <- df %>% filter(Age>input$Age_input[1], Age<input$Age_input[2]) %>% 
    filter(out==input$outcome_input) %>% filter(preg==input$pregnancy_input) %>% 
    ggplot(aes(x=Age,fill=preg))+
    geom_density()
  ggplotly(p2)
})
```

Column {data-width=500}
-----------------------------------------------------------------------

### What is Density Plot?

- A density plot is an alternative to Histogram used for visualizing the distribution of a continuous variable. The peaks of a Density Plot help to identify where values are concentrated over the interval of the continuous variable. Compared to Histograms, Density Plots are better at finding the distribution shape because they are re not affected by the number of bins used (each bar used in a typical histogram).

- For example, a Histogram with only 4 bins wouldn’t produce a distinguishable enough shape of distribution as a 30-bin Histogram would. However, with Density Plots, this isn’t an issue.

![](https://datavizcatalogue.com/methods/images/top_images/SVG/density_plot.svg)



